Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-24 manuscript.Rmd
Peer Review Ksenia

```{r, include = FALSE}
# import functions
source("functions.R") # good idea to source functions here~

@@

sjPlot::tab_model(null1) # Good to see that you are using this package. Tables look neat!
```

@@

>>>>

##data cleaning is very concise and efficient!!

```{r, include = FALSE}
# import functions
source("functions.R") ## semms very useful! Made a note for myself

@@

sjPlot::tab_model(null1)
```

@@

#probably a good idea to create a function that you can reuse, especially since random effect structure is the same
